Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-12-27 paper/paper.tex
NS referenced before properly defined, added a few words to make the text a bit clearer

However, \FIG{genotypes} also reveals stochasticity that is independent of viral genotype.
This stochasticity sometimes acts to the detriment of the virus, and sometimes to the detriment of the cell.
As an example of the former case, expressing unmutated copies of all eight genes does not guarantee a favorable outcome for the virus: for instance, the unmutated virion that infected \textit{cell 139} only expressed viral mRNA to 6\% of the total transcriptome, and the unmutated virion that infected \textit{cell 105} still induced IFN.
But in other cases, the stochasticity allows a clearly defective virus to still escape immune recognition.
For instance, there are a number of cells (e.g., \textit{cell 62} and \textit{cell 78}) that fail to activate IFN despite being infected by virions that fail to express NS.

@@

The viral defect most strongly associated with IFN induction was failure to express the NS gene (\FIG{genotypes}, \FIG{mutations}C).
Although it is sometimes possible to use complementing cells to generate influenza viruses lacking a specific gene~\citep{fujii2003selective,marsh2007specific}, we were unable to generate viruses that lacked NS.
The NS gene encodes two proteins (NS1 and NS2), the first of which is influenza's primary innate-immune antagonist~\citep{garcia1998influenza, hale2008multifunctional}.
We therefore mimicked the effect of absence of NS by creating a mutant virus (NS1stop) that had multiple stop codons early in the NS1 coding sequence.

>>>>

However, \FIG{genotypes} also reveals stochasticity that is independent of viral genotype.
This stochasticity sometimes acts to the detriment of the virus, and sometimes to the detriment of the cell.
As an example of the former case, expressing unmutated copies of all eight genes does not guarantee a favorable outcome for the virus: for instance, the unmutated virion that infected \textit{cell 139} only expressed viral mRNA to 6\% of the total transcriptome, and the unmutated virion that infected \textit{cell 105} still induced IFN.
But in other cases, the stochasticity allows a clearly defective virus to still escape immune recognition.
For instance, there are a number of cells (e.g., \textit{cell 62} and \textit{cell 78}) that fail to activate IFN despite being infected by virions that fail to express NS, the viral gene segment encoding the major interferon antagonist, NS1.

@@

The viral defect most strongly associated with IFN induction was failure to express the NS gene (\FIG{genotypes}, \FIG{mutations}C).
Although it is sometimes possible to use complementing cells to generate influenza viruses lacking a specific gene~\citep{fujii2003selective,marsh2007specific}, we were unable to generate viruses that lacked NS.
The NS gene encodes two proteins (NS1 and NS2), the first of which, as mentioned, is influenza's primary innate-immune antagonist~\citep{garcia1998influenza, hale2008multifunctional}.
We therefore mimicked the effect of absence of NS by creating a mutant virus (NS1stop) that had multiple stop codons early in the NS1 coding sequence.
